Multiple Linear Regression on Sleep Data

### 2025-05-08 paper/paper.qmd
commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
#Packages
library(tidyverse)
library(dplyr)
library(ggthemes)
library(tidyr)
library(knitr)
library(kableExtra)
library(car)
library(MASS)
library(readr)
library(janitor)
library(patchwork)
library(broom)
```

@@

```{r include=FALSE}
# 1. Model Selection using full_model_vif
model_backward <- step(test_model, direction = "backward")

@@

model_forward <- step(null_model, scope = full_scope, direction = "forward")
model_stepwise <- step(null_model, scope = full_scope, direction = "both")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
#Packages
library(tidyverse)
library(dplyr)
library(ggthemes)
library(tidyr)
library(knitr)
library(kableExtra)
library(car)
library(MASS)
library(readr)
library(janitor)
library(patchwork)
library(broom)
library(glmnet)
library(caret)
library(tidymodels)
library(rsample)
```

@@

```{r include=FALSE}
# 1. Model Selection using full_model_vif
model_backward <- stats::step(test_model, direction = "backward")

@@

model_forward <- stats::step(null_model, scope = full_scope, direction = "forward")
model_stepwise <- stats::step(null_model, scope = full_scope, direction = "both")

@@

For our suggested regression, we used LASSO regression. We hoped to extract the most import input features to achieve a simple yet powerful model. To find the optimal $\lambda$ or the regularization parameter, we used a cross-validation process by splitting our data set: train = 80%. We saw that `gender`, `occupation`, `bmi_category`, and `sleep_disorder` converged to zero.

```{r include=FALSE}
## Split Training/Test Data
sleep_sp <- sleep_test %>% initial_split(prop = 0.8, strata=sleep_duration)
rtrain <- sleep_sp %>% training()
rtest <- sleep_sp %>% testing()

model0 <- lm(sleep_duration ~ ., data=rtrain)
summary(model0)

## Regularization
xrtrain <- rtrain %>% dplyr::select(-sleep_duration) %>% as.matrix()
yrtrain <- rtrain$sleep_duration

xrtest  <- rtest %>% dplyr::select(-sleep_duration) %>% as.matrix()
yrtest  <- rtest$sleep_duration

modelL <- glmnet(xrtrain, yrtrain)
plot(modelL,label = TRUE)
## Df=# of nonzero coefficients, %Dev = % of Deviance explained (like SSR)
print(modelL)
## Coefficient for a certain lambda
coef.glmnet(modelL, s= 0.1)

## Cross-Validation
## nfolds = # of groups ex) 20
## Regression with 19 groups and test with 1 group
cvmodelL <- cv.glmnet(xrtrain, yrtrain, type.measure = "mse", nfolds = 20)
coef.glmnet(modelL, s= cvmodelL$lambda.min)
plot(cvmodelL)

coef_min_lambda <- coef.glmnet(modelL, s = cvmodelL$lambda.min)

# Convert to a tidy data frame and filter out zero coefficients
nonzero_coefs <- as.matrix(coef_min_lambda)
nonzero_coefs_df <- data.frame(
  Variable = rownames(nonzero_coefs),
  Coefficient = nonzero_coefs[, 1]
)

```

```{r}
kable(nonzero_coefs_df, digits = 4, caption = "Non-Zero Coefficients from LASSO (Selected by Cross-Validation)",
      row.names = FALSE)
```
